\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Rephrase start of abstract

\begin{abstract}
\zbf is a peer-to-peer system based on the BitTorrent protocol that uses WebRTC
to distribute content between peers. \zbf provides an easily accessible way for
developers to alleviate content delivery bandwidth concerns by marking DOM elements
such that \zbf will fetch these resources from peers with that resource. The \zbf
system has server-side tracker and WebRTC signaling channel components, as well
as client-side scripting that requests and delivers content between peers.
This version of the system implements basic chunking, parallelism, and fault tolerance.
In this paper, we describe the motivation for \zbf and the design and implementation of the
different components that comprise the system. We then detail future improvements
that could be made to increase the robustness and performance of the overall system.
\end{abstract}

>>>>

\begin{abstract}

\zbf is a peer-to-peer content delivery network. The system uses WebRTC to
cache and distribute content between peers. \zbf provides an easily accessible
way for developers to alleviate content delivery bandwidth concerns by marking
DOM elements such that \zbf will fetch these resources from peers with that
resource. The \zbf system has server-side tracker and WebRTC signaling channel
components, as well as client-side scripting that requests and delivers content
between peers. This version of the system implements basic chunking,
parallelism, and fault tolerance. In this paper, we describe the motivation for
\zbf and the design and implementation of the different components that
comprise the system. We then detail future improvements that could be made to
increase the robustness and performance of the overall system.

\end{abstract}
